Hydra Battles and Cie

### 2020-12-26 doc/part-hydras.tex
better definition of BoundedVariant (phase 2)

\begin{Coqsrc}
Class BoundedVariant (B:Battle) :=
  {
    mu:T1 ;
    m: Hydra -> T1;
    mu_nf: nf mu;
    Hvar: Hvariant T1_wf B m;
    m_bounded: forall h, m h t1< mu
  }.
\end{Coqsrc}

@@

\begin{Coqsrc}
Section Bounded.
  Context (B: Battle) (Hy : BoundedVariant B).

@@

  Context (Var : BoundedVariant free ).
  \end{Coqsrc}

@@

\begin{Coqanswer}
  Impossibility_free
     : BoundedVariant free -> False
\end{Coqanswer}
%%% ICI

@@

\subsection{Back to Hydras}
\label{sec:standard-battles-cases}
We are now able to complete our proof that there exists no bounded variant for proving the termination of standard hydra battles. This proof can
be consulted in the module 
\url{../theories/html/hydras.Hydra.Epsilon0_Needed_Std.html}.
Please note that it has the same global structure as in section\ref{sec:free-battles-case} 
% ICI !
Applying the  lemmas  \texttt{Lemma2\_6\_1} of the module 
\href{../theories/html/hydras.Epsilon0.Paths.html\#Lemma2_6_1}%
{\texttt{Lemma2\_6\_1}}   and 
\href{../theories/html/hydras.Epsilon0.Paths.html\#constant_to_standard_path}%
{\texttt{constant\_to\_standard\_path}},
we can convert any inequality $\beta<\alpha<\epsilon_0$ into a standard path from
$\alpha$ to  $\beta$, then into a fragment of a standard battle from 
$\iota(\alpha)$ to $\iota(\beta)$.

@@

  Context (Var : BoundedVariant standard).
 \end{Coqsrc}

>>>>

\begin{Coqsrc}
Class BoundedVariant {A:Type}{Lt:relation A}
      {Wf: well_founded Lt}{B : Battle}
      {m: Hydra -> A} (Var: Hvariant  Wf  B m)(mu:A):=
  {
  m_bounded: forall h, Lt (m h ) mu
  }.
\end{Coqsrc}

@@

\begin{Coqsrc}
Context (B: Battle)
          (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf B m)
          (Hy : BoundedVariant  Var mu).

@@

  Context (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf free m)
          (Hy : BoundedVariant Var mu).
  \end{Coqsrc}

@@

\begin{Coqanswer}
Impossibility_free
     : forall (mu : T1) (m : Hydra -> T1) (Var : Hvariant T1_wf free m),
       BoundedVariant Var mu -> False
\end{Coqanswer}
%%% ICI

@@

\subsection{Back to Hydras}
\label{sec:standard-battles-cases}
We are now able to complete our proof that there exists no bounded variant for proving the termination of standard hydra battles. This proof can
be consulted in the module 
\url{../theories/html/hydras.Hydra.Epsilon0_Needed_Std.html}.
Please note that it has the same global structure as in section\ref{sec:free-battles-case} 
% ICI !
Applying the  lemmas  \texttt{Lemma2\_6\_1} of the module 
\href{../theories/html/hydras.Epsilon0.Paths.html\#Lemma2_6_1}%
{\texttt{Epsilon0.Paths}}   and 
\href{../theories/html/hydras.Epsilon0.Paths.html\#constant_to_standard_path}%
{\texttt{constant\_to\_standard\_path}},
we can convert any inequality $\beta<\alpha<\epsilon_0$ into a standard path from
$\alpha$ to  $\beta$, then into a fragment of a standard battle from 
$\iota(\alpha)$ to $\iota(\beta)$, hence the inequality $m(\iota(\beta))<m(\iota(\alpha))$.

@@

Context (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf standard m)
          (Hy : BoundedVariant Var mu).
 \end{Coqsrc}
